%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgments}{acknowledgments}
\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgments}

First and foremost, we would like to express our sincere gratitude to our advisors, Dr.~T Sundararajan and Dr.~Pramod Kuntikana for their guidance, patience, motivation, and continuous support during the course of our project and smooth completion of the course. We would also like to thank Indian Institute of Technology Palakkad for giving chance to do this course project as part of Measurements in Thermofluids course.

We would like to express sincere gratitude to all the teaching assistants and our co research scholars Mr. Ajith U K Nair, Mr. Arundas Odungat, Mr. Vaishak Rajendran Pillai, Mr. Ragupathi A P, Mr. Ubaidulla C T, Mr. Muruga Prabu U, special mention to Mr. Sabareesh V for their valuable support and guidance throughout semester for smooth completion of lab experiments and their valuable insights and discussions for completion of this course project.

We would like to thank other faculty members of Department of Mechanical Engineering special mention to Dr. Anoop Akkoorath Mana, Dr. Dinesh Setti, Dr. Kanmani Subbu, Dr. Ganesh Natarajan and Dr. Vineed Narayanan for their valuable support, guidance and their help at various stages of this project. We would also like to thank all the staffs of Mechanical Engineering especially Mr. Bharath Krishna and  Mr. Ganesha for helping us at different stages of this project.

We would like to thank CSquare Innovation Lab of IIT Palakkad, Chief Innovation officer Dr. Jacob Chandapillai for providing facilities for fabrication of experimental setup. We would also like to thank staffs of CSquare Innovation lab, Mr. Pradeep and Mr. Vinod for their help during fabrication in lab.

Last but not the least, we would like to express our sincere gratitude to our family members for their unconditional love, support, motivation and encouragement. We would also like to thank the Almighty for smooth completion of our project.

\endgroup
