%******************************************************************
% List of Symbols
% If you do not want this, comment out all contents of this file 
%******************************************************************
\pdfbookmark[1]{List of Symbols}{List of Symbols}
\nomenclature{$U$}{Velocity of air flow.}
\nomenclature{$\Delta P$}{Differential pressure.}
\nomenclature{$\rho$}{Density of air.}
\nomenclature{$E$}{Voltage across the sensor.}
\nomenclature{$E_0$}{Voltage across the sensor in no flow condition.}
\nomenclature{$B,~n$}{Numerical constants used in King's law.}
\nomenclature{$q$}{Number of sample spaces.}
\nomenclature{$\sigma$}{Standard deviation.}
\nomenclature{$\tau$}{Time constant.}
\nomenclature{$D$}{Diameter of the solid cylinder.}
\nomenclature{$v$}{Velocity of the flow in temporal domain.}
\nomenclature{$\Hat{V}$}{Velocity of the flow in frequency domain.}
\nomenclature{$\omega$}{Frequency in rad/s.}
\nomenclature{$Re$}{Reynolds number.}
\nomenclature{$St$}{Strouhal number.}
\nomenclature{$f$}{Frequency in Hz.}
\nomenclature{$\mu$}{Dynamic viscosity of air.}
\nomenclature{$\rho$}{Density of air.}
\nomenclature{$L_{\text{settling}}$}{Length of the settling chamber.}
\nomenclature{$W_{\text{settling}}$}{Width of the settling chamber.}
\nomenclature{$W_{\text{contraction}}$}{Width of the contraction section.}
\nomenclature{$H_{\text{contraction}}$}{Height of the contraction section.}
\nomenclature{$L_{\text{contraction}}$}{Length of the contraction section.}
\nomenclature{$W_{\text{test}}$}{Width of the test section.}
\nomenclature{$L_{\text{test}}$}{Length of the test section.}
\nomenclature{$H_{\text{test}}$}{Height of the test section.}
\nomenclature{$W_{\text{diffuser}}$}{Width of the diffuser section.}
\nomenclature{$L_{\text{diffuser}}$}{Length of the diffuser section.}
\nomenclature{$H_{\text{diffuser}}$}{Height of the diffuser section.}
\nomenclature{$R$}{Resistance of the wire.}
\nomenclature{$\rho_w$}{Resistivity of the wire.}
\nomenclature{$L_w$}{Length of the wire.}
\nomenclature{$A_w$}{Area of cross section of the wire.}
\nomenclature{$I$}{Current through the wire.}
\nomenclature{$h$}{heat transfer coefficient of the wire.}
\nomenclature{$T_{\text{wire}}$}{Maximum operating temperature of the wire.}
\nomenclature{$T$}{Ambient temperature.}
\nomenclature{$A_{\text{diffuser}}$}{Area of cross section of the diffuser section.}
\nomenclature{$A_{\text{contraction}}$}{Area of cross section of the contraction section.}
\nomenclature{$A_{\text{test}}$}{Area of cross section of the test section.}
\nomenclature{$A_{\text{straws}}$}{Contact area of straw with the air.}
\nomenclature{$Q$}{Air flow rate in the wind tunnel.}
\nomenclature{$\Delta P_{\text{settling}}$}{Pressure drop in the settling chamber.}
\nomenclature{$\Delta P_{\text{contraction}}$}{Pressure drop in the contraction section.}
\nomenclature{$\Delta P_{\text{test}}$}{Pressure drop in the test section.}
\nomenclature{$\Delta P_{\text{diffuser}}$}{Pressure drop in the diffuser section.}
\nomenclature{$V_m$}{Maximum velocity of the air.}
\nomenclature{$k_{\text{settling}}$}{Loss factor in the settling chamber.}
\nomenclature{$k_{\text{contraction}}$}{Loss factor in the contraction section.}
\nomenclature{$k_{\text{diffuser}}$}{Loss factor in the diffuser section.}
\nomenclature{$f_f$}{friction factor in the test section.}
\nomenclature{$D_h$}{Hydraulic diameter of the test section.}
\nomenclature{$\Delta P_{\text{total}}$}{Total pressure drop in the wind tunnel.}
\nomenclature{$\eta$}{Efficiency of the fan.}
\nomenclature{$P_{\text{fan}}$}{Power of the suction fan.}

\printnomenclature 